Automated Verification of Stand-Alone Solar Photovoltaic Systems

### 2018-11-23 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

\author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
\thanks{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
\thanks{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
\thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support.}
\thanks{Manuscript received November 21, 2018; revised XXXXX 11, 2019.}}

@@

In prior studies, the evaluation of PV systems w.r.t. user requirements were performed by software simulation tools using MATLAB/Simulink~\cite{Benatiallah2017}, \cite{Samrat2014}, and \textcolor{red}{Tool name?}~\cite{Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}. Some related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and to maximize the power point of solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification and they restrict themselves to solar panels or smart grids. 
%
In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels, where the focus has been on the modeling of the dynamics of PV panels and their interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}. Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.

@@

%The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage. %MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power. Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime. 
%
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%
%
%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components. The use of battery as a storage form implies thus the presence of a charge controller. 
%
In general, there are two main operating modes for the controller \textcolor{red}{add citation here}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.

>>>>

\author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
\thanks{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
\thanks{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}% <-this % stops a space
\thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support.}
\thanks{Manuscript received November 23, 2018; revised XXXXX 11, 2019.}}

@@

In prior studies, the evaluation of PV systems w.r.t. user requirements were performed by software simulation tools using \textcolor{blue} {MATLAB/Simulink~\cite{Benatiallah2017, Samrat2014, Natsheh2012}}, or HOMER Pro \cite{Lamnadi2017}. Some related studies were carried out toward the formal modeling of power smart grids~\cite{Akram2018} and to maximize the power point of solar panels~\cite{Driouich2017}; however, those studies do not perform automated formal verification and they restrict themselves to solar panels or smart grids. 
%
In addition, recent research that applies formal verification to solar energy, has attempted to formalize and implement a formal study of large population of PV panels, where the focus has been on the modeling of the dynamics of PV panels and their interaction with the grid, without batteries~\cite{Abate2017}; or to model a PV system in Modelica, to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}. Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.

@@

%The charge controller or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage. %MPPT, or maximum power point tracking, is an electronic control mechanism that maintains the PV operating at the voltage of maximum power. Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime. 
%
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%
%
%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components. The use of battery as a storage form implies thus the presence of a charge controller. 
%
In general, there are two main operating modes for the controller \textcolor{blue} {\cite{Rawat}}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values.
